### 2023-02-06 article.tex
Improve

\paragraph{Code must be reviewed}

@@

\paragraph{Code must be clean}

@@

\paragraph{Code must be hosted}

@@

\paragraph{Code must be tested}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Publishing raw code}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \paragraph{The problems with hosted code}

Albeit hosted code is vastly superior over raw code
in case of reproduciblity and correctness,
there are some problems with hosted code as well.
The most important one is that hosted code needs maintanance:
the libraries that are used by an experiment
will change over time, inevitably causing the experiment to fail
over time. 
The degradation of software is a known feature for nearly 
four decades (see the definition of 'bit rot' at \cite{steele1983hacker}),
here a more modern (and in this context superior)
definition is used: software collapse \cite{hinsen2019dealing},
in which software fails due to dependencies on other 
software.
Where that paper recommends using older software foundations 
with multiple implementations \cite{hinsen2019dealing},
this paper recommends a modern solution that potentially has more longevity:
to publish the code installed in a virtual environment
(including the dependencies used at that time), as described below.

There is another problem that authors of academic code face,
which is that they may be contacted with a user 
asking for technical report 
(against which a 'no' is just fine \cite{barnes2010publish})
or -more relevant to the research- sending in a bug report.
One solution for the author is to ignore such emails
and it can be argued that no energy should be wasted on published code
and work on something new instead 
(see \cite{barnes2010publish} for a better way to deal with the problem).
However, upon the find of a new bug, the question is:
does all the research that use that software still 
result in the same conclusions?
To prevent authors chosing to hide bug reports, 
a code hosting website usually has a public place to report bugs,
to increase transparency in the handling of bug reports.

% \paragraph{Suggestions for knowledge management}

Here are multiple suggestions to make hosted code FAIR.
To make the hosted code findable, commonly a paper refers to its URL.
At the homepage of hosted code (e.g. a GitHub repository), 
there is no standardized metadata, to,
for example, link to the paper.
Using a popular code host ensures the code is easily accessible.
There is some interoperabily supplied by a version control manager,
such as in obtaining the history of the code.
The reusability of code is reasonably easy to assess, 
by using so-called build badges.
However, there is no guarantee that a build badge that claimes success,
actually is an honest signal (i.e. that code may not actually build),
nor are there standards for what 'success' entails.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Publishing a virtual environment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% \paragraph{Containers allow for runnable code, for longer periods of time}

@@

% \paragraph{Runnable code can precisely reproduce an experiment}

@@

% \paragraph{Runnable code allows others to re-use an experiment}

@@

% \paragraph{The problems with runnable code}

% \paragraph{Suggestions for knowledge management}

@@

>>>>

\paragraph{Code must be reviewed to ensure the correct amount of documentation}

@@

\subsubsection{Code must be clean}

@@

\subsubsection{Code must be hosted}

@@

\subsubsection{Code must be tested}

@@

\paragraph{Publishing a virtual environment}

@@

\paragraph{Containers allow for runnable code, for longer periods of time}

@@

\paragraph{Runnable code can precisely reproduce an experiment}

@@

\paragraph{Runnable code allows others to re-use an experiment}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Making code FAIR data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Suggestions for knowledge management}

@@

In a perfect world, all code has the characteristis of ideal paradata
and is written from software development best practices.
This section discusses the problems that arise by doing so.

\paragraph{Need more training}

\paragraph{Code needs maintanance}

Code needs maintanance:
the libraries that are used by an experiment
will change over time, inevitably causing the experiment to fail
over time. 
The degradation of software is a known feature for nearly 
four decades (see the definition of 'bit rot' at \cite{steele1983hacker}),
here a more modern (and in this context superior)
definition is used: software collapse \cite{hinsen2019dealing},
in which software fails due to dependencies on other 
software.
Where that paper recommends using older software foundations 
with multiple implementations \cite{hinsen2019dealing},
this paper recommends a modern solution that potentially has more longevity:
to publish the code installed in a virtual environment
(including the dependencies used at that time), as described below.

\paragraph{Authors can be contacted}

There is another problem that authors of academic code face,
which is that they may be contacted with a user 
asking for technical report 
(against which a 'no' is just fine \cite{barnes2010publish})
or -more relevant to the research- sending in a bug report.
One solution for the author is to ignore such emails
and it can be argued that no energy should be wasted on published code
and work on something new instead 
(see \cite{barnes2010publish} for a better way to deal with the problem).

\paragraph{How to handle bugs?}

However, upon the find of a new bug, the question is:
does all the research that use that software still 
result in the same conclusions?
To prevent authors chosing to hide bug reports, 
a code hosting website usually has a public place to report bugs,
to increase transparency in the handling of bug reports.

\paragraph{The problems with runnable code}
